### 2014-06-03 ACL2014/experiments.tex
updating experiment section

In the first experiment, we vary the similarity threshold parameter $\tau$ to be in $\{0.7,0.8,0.9\}$ 
while fixing $K=16$ and $L=10$ for the \aol and \dataA datasets. 
Table~\ref{tab:varyTau} shows that as expected, finding near-duplicates, when $\tau=0.9$, 
is easier than finding nearest neighbors when $\tau=0.7$. For, rest of this paper, 
we fix $\tau=0.7$ as we are interested in both near-duplicates and nearest-neighbors for our test queries.

>>>>

In the first experiment, we vary the similarity threshold parameter $\tau$ to be in $\{0.7,0.8,0.9\}$ 
while fixing $K=16$ and $L=10$ for the \aol and \dataA datasets. 
From Table~\ref{tab:varyTau}, $\tau=0.9$ achieves higher recall than that of $\tau=0.7$.
This is expected as finding near duplicates is easier than finding near neighbors. For, rest of this paper, 
we fix $\tau=0.7$ as we are interested in both near-duplicates and nearest-neighbors for our test queries.
